---
title: "Using the `powers` package"
author: "Divita Pal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette

__Note__: This package was developed only for Assignment purpose.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! 

```{r}
library(powers)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)

lapply(my_list, function(x) x^2)

lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Wow!!!


Examples for boxcox fuctions

```{r}
x <- 1:20
p <- -2.5
y <- boxcox(x,p)
plot(x,y)
```



```{r}
x <- 1:20
p <- 2.5
y <- boxcox(x,p)
plot(x,y)

````


```{r}
x <- 1:20
p <- 0
y <- boxcox(x,p)
plot(x,y)
```

The above three plots shows the usage of the boxcox functions. When p=0, the value of the function is given by `log(x)` The plot for `p<0` is almost a constant except in the start. The plot for `p>0` shows that the value of the function increases with increasing x regardless of p.
